\documentclass{article}
\title{Uniting Twist Developer Documentation}
\author{Nick Werle}

\begin{document}
\maketitle
\section{Activities}
Uniting twist contains two activities: \texttt{MainActivity} and \texttt{StartActivity}. Each has an associated layout of the same name.

\subsection{StartActivity}
The start activity is the "main menu" of sorts - where the player "begins" the game. Displays the high score and starts the MainActivity

\subsection{MainActivity}
The main activity is the main portion of the app - the activity where the game is played. Provides logic for setting up renderer, losing.

\section{Classes}
\subsection{MyGlRenderer}
Implementation for \texttt{GLSurfaceView.Renderer}. Provides methods to set up the shader, debug methods for open GL errors, etc.

\subsection{Point}
Basic XYZ point implementation.

\subsection{Scene}
Holds the scene to be drawn, as well as update and pause/resume methods to handle ticks. 

\subsection{Hexagon}
Object that handles the rendering an individual hexagon. Not for game logic.

\subsection{GyroscopeListener}
Listens to the Gyroscope for \texttt{onSensorChanged} events, updating the angle and time of each event.

\subsection{GraphGameHexagon}
Handles the graph that controls which hexagons are connected to which. 

\subsection{GameHexagonContainer}
Holds a GameHexagon and the point it exists at. Provides a method to draw the hexagon.

\subsection{GameHexagon}
Object containing each hexagon as an object of the game (as opposed to one for rendering). Provides logic for moving, rotating, and drawing itself on screen.

\subsection{GameField}
Handles the hexagons that fly about the screen and the graph of connected hexagons too. Spawns hexagons on a timer, detects collisions of hexagons, and updates hexagons each tick.

\subsection{FlyingGameHexagon}
A GameHexagonContainer for hexagons that are still in flight. Updates it's position based on the angle and  time since last update.

\subsection{FieldGraph}
Closely related to the \texttt{GameGraphHexagon}. Handles the game graph in relation to the hexagons on the field. Handles logic for removing clusers, rotating the field, and drawing.

\subsection{Engine}
Handles tick logic, updating the scene and then rendering each tick. Accomplishes this by recording the time of the last tick and then attempting to rerender when a minimum amount of time has elapsed.

\subsection{ColorUtils}
Color related utilities.

\subsection{Circle}
Draws the circle which defines the radius the player's placed tiles may not exceed.
\end{document}
